\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-01 manuscript.Rmd

```{r figCor,out.width="50%",fig.cap= "Iter-correlation of the items",results='asis'}

@@

```{r include=FALSE}
fa.diagram(fa.5F.4,sort=TRUE,labels=NULL,flabels=NULL,cut=.3,
                 simple=TRUE,errors=F,
                 digits=1,e.size=.1,rsize=3,side=2,main= "Five Factor Solution Oblique",cex=NULL,color.lines=TRUE,
                 marg=c(.5,.5,1.5,.5),adj=2) 
```

```{r minres 5 factor supplimentary analyisis, eval=FALSE, include=FALSE}
fa.5F.min.1 <- fa(r=correlations$rho, nfactors = 5, fm= "minres",rotate ="varimax",
                residuals = TRUE, SMC = TRUE, n.obs =428)
EE <- print(fa.5F.min.1, cut = .3, digits = 3, sort = TRUE)

@@

```{r EFA 6 Factors Promax, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='hide'}
#LB.factor <- sapply(LB, as.factor)
#correlations <- polychoric(LB.factor, correct = 0)

@@

```{r factordetails, include=FALSE}
Fac.5 <- fa.5F.4 
#Commonality
min.com <- min(Fac.5$communality)
max.com <- max(Fac.5$communality)

# factor loadings

Factorloading <- cbind(Fac.5$loadings, Fac.5$communality)
colnames(Factorloading)= c("F1", "F2","F3", "F4", "F5", "Communalities")

min.loadings <- abs(min(Fac.5$loadings))
max.loadings <- max(Fac.5$loadings)

@@

apa_table(unclass(Factorloading))
```

>>>>

```{r figCor,out.width="50%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}

@@

```{r EFAplotcode, include=FALSE}
#library(DiagrammeR)
EFAplot.LR <- grViz("
digraph boxes_and_circles {

graph [layout = dot,rankdir = LR, fontsize = 40]

# node definitions with substituted label text
node [fontname = Helvetica, shape = circle,  margin = 0.5, width = 3.5, height = .5,
fixedsize = true, fontsize = 35]
F1 [label = 'Blue 
Filter']
F2 [label = 'Natural 
Light']
F3 [label = 'Sleep
Environment']
F4 [label = 'Cell Phone']
F5 [label = 'Awareness']
node [fontname = Helvetica, shape = box]
b [label = 'item43']
c [label = 'item26']
d [label = 'item32']
e [label = 'item10']
f [label = 'item47']
g [label = 'item36']
h [label = 'item44']
i [label = 'item35']
j [label = 'item13']
k [label = 'item14']
l [label = 'item41']
m [label = 'item7']
n [label = 'item27']
o [label = 'item21']
p [label = 'item34']
q [label = 'item19']
r [label = 'item2']
s [label = 'item5']
t [label = 'item24']
u [label = 'item30']
v [label = 'item1']
w [label = 'item16']
x [label = 'item28']

{rank = same; F1 F2 F3 F4 F5}
# edge definitions with the node IDs
edge [fontname = Helvetica, fontsize = 35]
F1 -> b[label = '0.99']
F1-> c [label = '0.93']
F1-> d [label = '0.80']
F2 -> e [label = '0.82']
F2 -> f[label = '0.82']
F2 -> g [label = '0.63']
F2 -> h[ label = '-0.47', color =red]
F2 -> i [label = '0.46']
F2 -> j [label = '0.34']
F3 -> k [label = '0.89']
F3 -> l [label = '0.70']
F3 -> m [label = '0.66']
F3 -> n [label = '0.38']
F3 -> o [label = '-0.34', color =red]
F4 -> p [label = '0.84']
F4 -> q [label = '0.80']
F4 -> r [label = '0.69']
F5 -> s [label = '0.69']
F5 -> t [label = '0.54']
F5 -> u [label = '0.52']
F5 -> v [label = '0.35']
F5 -> w [label = '0.31']
F5 -> x [label = '0.31']

}
")

export_svg(EFAplot.LR) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("EFAplot.LR.png")

```{r EFAplot,  fig.cap='Five Factor Solution', fig.align='center', out.width= "120%", out.height= "100%", warning=FALSE}
knitr::include_graphics('EFAplot.LR.png')

```{r minres 5 factor supplimentary analyisis, eval=FALSE, include=FALSE}

#Supplementary EFA with Minres Extraction

fa.5F.min.1 <- fa(r=correlations$rho, nfactors = 5, fm= "minres",rotate ="varimax",
                residuals = TRUE, SMC = TRUE, n.obs =428)
EE <- print(fa.5F.min.1, cut = .3, digits = 3, sort = TRUE)

@@

```{r EFA 6 Factors Promax, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='hide'}
# EFA with 6 factor (rejected)

#LB.factor <- sapply(LB, as.factor)
#correlations <- polychoric(LB.factor, correct = 0)

@@

```{r factordetails, include=FALSE}
#Preparing the EFA table

factor.des = matrix(, nrow = 24, ncol = 6)
as.table(factor.des)
rownames(factor.des) <- c("item43", "item26",  "item32",   
                          "item10",  "item47",  "item36", "item44",  "item35",  "item13", 
                          "item14", "item41",  "item7","item27","item21",
                          "item34", "item19", "item2",
                          "item5", "item24", "item30", "item1", "item16", "item28","% of variance")

colnames(factor.des) <- c("F1", "F2", "F3", "F4", "F5", "Communality")

factor.des[,1] <- c(.99, .93, .80, "-","-","-","-","-","-","-","-","-","-","-","-",
                    "-","-","-","-","-","-","-","-", 11)

factor.des[,2] <- c("-", "-", "-", .82,.82,.63,-.47,.46,.34,"-","-","-","-","-","-",
                    "-","-","-","-","-","-","-","-", 10)

factor.des[,3] <- c("-", "-", "-", "-","-","-","-","-","-",.89,.70,.66,.38,-.34,"-",
                    "-","-","-","-","-","-","-","-", 9)

factor.des[,4] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-",.84,
                    .80,.67,"-","-","-","-","-","-", 9)

factor.des[,5] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-","-","-","-"
                    ,.69,.54,.52,.35,.31,.31, 6)

factor.des[,6] <- c (.99, .90,.67,.68,.70,.45,.24,.24,.13,.81,.60,.45,.21,.12,.74,.64,.54,
                     .51,.33,.29,.13,.21,.10, "-")

#Commonality
Fac.5 <- fa.5F.4
min.com <- min(Fac.5$communality)
max.com <- max(Fac.5$communality)

# loadings
min.loadings <- min(Fac.5$loadings)
max.loadings <- max(Fac.5$loadings)

@@

apa_table(factor.des,align = "c", note = "Only loading higher than .30 is reported")
```
